\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2018-09-28 paper/manuscript.tex
addressed the point on javascript by stating in a footnote that this problem, if anything, should lead to a more balanced sample

To download the websites, we rely on the Unix command line tool \texttt{wget}. This program is used to download files from the Internet, and with the use of a recursive option, acts like a web crawler and scraper. This means that \texttt{wget} downloads HTML files, parses them and then follows the links contained therein. Then it follows those links and repeats the process until it has constructed a complete tree of the website (note that the program is instructed to stay on the same domain, i.e. it does not follow external links). This way, all the files that make up a website are downloaded. For some cities, whose websites make heavy use of JavaScript to serve content dynamically, such content is not reachable with our methodology and would require additional steps to obtain. For this paper, we ignore such sites and restricted our corpus to cities with at least three successfully downloaded pages.

>>>>

To download the websites, we rely on the Unix command line tool \texttt{wget}. This program is used to download files from the Internet, and with the use of a recursive option, acts like a web crawler and scraper. This means that \texttt{wget} downloads HTML files, parses them and then follows the links contained therein. Then it follows those links and repeats the process until it has constructed a complete tree of the website (note that the program is instructed to stay on the same domain, i.e. it does not follow external links). This way, all the files that make up a website are downloaded. For some cities, whose websites make heavy use of JavaScript to serve content dynamically, such content is not reachable with our methodology and would require additional steps to obtain. For this paper, we ignore such sites and restricted our corpus to cities with at least three successfully downloaded pages.\footnote{There is a possibility that this leads to a small bias in selecting against cities with the resources to build more elaborate websites. However, given that our sample is generally more on the wealthy side, this, if anything, should lead to a more balanced sample.}
